Research Notes

### 2018-02-19 writups/notes.tex
stuff is working

We can use this extra degreee of freedom to specify $P(z = L) = P_L$ some
constant. Then we can just simulate away! Let's choose $L = 10, k_x = k_z = 1, H
= 10, g = 10$ which constrains $N^2 \equiv g/H = 1, \omega^2 = \frac{1}{2 +
1/400}$.

>>>>

We can use this extra degreee of freedom to specify $P(z = L) = 0$ so the
oscillations should have zero mean. Then we can just simulate away!

Since we're much more interested in the $z$ behavior, we will set the $z$ axis
to be further away. Let's choose $\rho_0 = 1, L_x = 10, L_z = 20, k_x = 2, k_z =
1, H = 5, g = 10$ which constrains $N^2 \equiv g/H = 1, \omega^2 = \frac{4}{5 +
1/100}$. Some considerations:
\begin{itemize}
    \item $\frac{1}{k_xH}, \frac{1}{k_zH}$ are $1/10, 1/5$ respectively,
        small-ish but $L_Z = 8H$ so we should be able to see the $e^{z/2H}$
        behavior well.

    \item The vertical phase velocity is $\frac{\omega}{k_z} \sim 1$, so we
        should simulate at least out to $t = 20$ for the wave to fully propagate
        to the boundary.
\end{itemize}
